The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-10 paper/ms.tex
add in tim's figure

From visual inspection of the power spectra, HD 181069, HD 183124, HD 182354, HD 182692, and HD 180658 are seen to be core helium-burning red clump stars.

>>>>

From visual inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be core helium-burning red clump stars. A power spectrum of the best example of these, HD~183124, is shown in Figure~\ref{HD_183124}.

\begin{figure*}
\noindent\includegraphics[width=19cm,keepaspectratio]{HD_183124.png}

\caption{\label{HD_183124}
Power spectrum (left) and \'{e}chelle diagram (right) of the solar-like oscillations of the red clump star HD~183124. The modes in the power spectrum used for the \'{e}chelle diagram are highlighted with blue dots. In the \'{e}chelle diagram we see the characteristic pattern of `bumped' modes from avoided crossings between the comb of \emph{p}-modes and \emph{g}-mode oscillations with a period spacing of $\Delta \Pi = 300.1~\text{s}$.}
\end{figure*}
